### 2014-12-24 Neutral_simulPow.Rmd
minor corrections sent to peerj preprints
Add color figures

@@

# Plot of the spatial pattern for Neutral model with Logseries SAD with 8,64,256 species and side=512/256
#
g <- plotNeutral_SpatPat(64,256,500,"L",c(0.1,1))
g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.01,0.1,1))
g

@@

### Plot Average SAD!
setwd("Simul")
den <- plotNeutral_SAD(0,256)

>>>>

I use here the following neutral model with exponential dispersion:

<https://github.com/lsaravia/Neutral>

@@

# Plot of the spatial pattern for Neutral model with Logseries SAD with 8,64,256 species and side=512/256
#
#g <- plotNeutral_SpatPat(64,256,500,"L",c(0.1,1))
g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.01,0.1,1))
g

@@

### Plot Average SAD!
setwd("Simul")
detach("package:dplyr", unload=TRUE)
den <- plotNeutral_SAD(0,256)

### 2014-12-24 SP_simul.Rmd
Add figures of neutral spatpatt Dq & RAD
minor corrections sent to peerj preprints
Add color figures

@@

>>>>

I use mfSBA for multifractal estimation: <https://github.com/lsaravia/mfsba>

@@

zq <- readDq_fit(256,8,"Logseries")
g <-plotDqFitG(zq)
g
setwd(oldcd)
ggsave("DqFit_Logser_8_256.png", width=8,height=6,units="in",dpi=600)

setwd("Simul")
zq <- readDq_fit(256,256,"Logseries")
g <-plotDqFitG(zq)
g
setwd(oldcd)
ggsave("DqFit_Logser_256_256.png", width=8,height=6,units="in",dpi=600)
